### 2019-06-30 Memoria/Chapters/ExperimentalResults.tex
Acabada memoria excepto conclusiones y trabajo futuro

This chapter presents the results obtained by the two new proposals introduced in this work (in Chapter \ref{ch:NewProposals}) and those obtained by the state-of-the-art. Being the mentioned its main purpose, we firstly introduce a brief study on the influence of the parameter $\xi$ in the \acs{DILS} method in Section \ref{sec:XiInfl}, so the reader gets a better comprehension of theory presented in Section \ref{sec:DILS}. Afterwards we will carry out an in-depth comparison between \acs{BRKGA}$_{CC}$ and \acs{SHADE}$_{CC}$ in Section \ref{sec:BRKGAvsSHADE}, as both are population-based and heuristic-guided methods. Finally, in Section \ref{sec:NewPropvsSOTA}  we will present a more general comparison that will include all state-of-the-art methods and the new proposals.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.2}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{l ccc c ccc}
			\hline
			\multirow{2}{*}{Dataset} &
			\multicolumn{3}{c}{\acs{BRKGA}$_{CC}$} &&  \multicolumn{3}{c}{\acs{SHADE}$_{CC}$} \\
			\cline{2-4} \cline{6-8}
			& \acs{ARI} & Unsat(\%) & Time(s) && \acs{ARI} & Unsat(\%) & Time(s) \\
			\hline
			Appendicitis & 1.000 & 0.000 & 389.905 && 1.000 & 0.000 & 371.579 \\
			Breast Cancer & 0.807 & 9.086 & 4061.162 && \textbf{0.977} & 0.891 & 3984.370 \\
			Bupa & 0.936 & 2.975 & 1529.151 && \textbf{0.993} & 0.281 & 1508.772 \\
			Circles & 0.935 & 2.814 & 1180.268 && \textbf{1.000} & 0.000 & 1170.452 \\
			Ecoli & 0.028 & 25.716 & 1267.419 && \textbf{0.047} & 21.466 & 1277.903 \\
			Glass & 0.038 & 23.610 & 766.861 && \textbf{0.082} & 16.412 & 796.162 \\
			Haberman & 0.943 & 2.073 & 1266.131 && \textbf{0.997} & 0.138 & 1235.441 \\
			Hayesroth & \textbf{0.548} & 6.331 & 554.339 && 0.531 & 7.056 & 540.585 \\
			Ionosphere & 0.902 & 4.314 & 2051.251 && \textbf{0.993} & 0.258 & 2019.558 \\
			Iris & \textbf{0.691} & 5.241 & 513.675 && 0.553 & 6.528 & 488.262 \\
			Monk2 & 0.855 & 6.025 & 2055.425 && \textbf{0.991} & 0.379 & 2013.468 \\
			Moons & 0.937 & 2.689 & 1177.848 && \textbf{0.995} & 0.158 & 1157.222 \\
			Saheart & 0.881 & 5.250 & 2402.513 && \textbf{0.981} & 0.706 & 2353.931 \\
			Sonar & 0.992 & 0.186 & 1138.769 && \textbf{1.000} & 0.000 & 1127.020 \\
			Soybean & 0.416 & 0.000 & 171.281 && \textbf{0.563} & 0.000 & 153.406 \\
			Spectfheart & 0.953 & 1.677 & 1602.229 && \textbf{1.000} & 0.000 & 1526.925 \\
			Spiral & 0.921 & 3.604 & 1178.580 && \textbf{0.998} & 0.091 & 1155.194 \\
			Tae & 0.351 & 9.807 & 527.292 && \textbf{0.392} & 9.419 & 508.610 \\
			Vowel & 0.002 & 14.682 & 5450.331 && \textbf{0.003} & 13.766 & 5514.052 \\
			Zoo & \textbf{0.176} & 5.429 & 335.715 && 0.153 & 4.191 & 320.186 \\
			\hline
			Mean & 0.666 & 6.575 & 1481.007 && \textbf{0.713} & 4.087 & 1461.155 \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.2}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lcccccccc}
			\hline
			Dataset & \acs{SHADE}$_{CC}$ & \acs{DILS}$_{CC}$ & \acs{BRKGA}$_{CC}$ & \acs{COPKM} & \acs{LCVQE} & \acs{RDPM} & \acs{TVClust} & \acs{CECM} \\
			\hline
			Appendicitis & 0.086 & 0.611 & 0.022 & - & 0.335 & 0.316 & 0.025 & -0.005 \\
			Breast Cancer & 0.159 & 0.755 & 0.395 & -0.604 & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & 0.104 & 0.870 & 0.281 & - & -0.005 & -0.005 & -0.004 & -0.011 \\
			Circles & 0.063 & 0.798 & 0.166 & - & -0.003 & 0.162 & 0.137 & 0.133 \\
			Ecoli & 0.020 & 0.069 & 0.009 & - & 0.387 & 0.417 & 0.265 & - \\
			Glass & 0.013 & 0.009 & 0.016 & 0.184 & 0.268 & 0.197 & 0.211 & - \\
			Haberman & 0.084 & 0.638 & 0.047 & - & -0.002 & 0.127 & 0.218 & -0.004 \\
			Hayesroth & 0.025 & 0.031 & 0.027 & - & 0.106 & 0.097 & 0.054 & 0.139 \\
			Ionosphere & 0.332 & 0.792 & 0.125 & - & 0.168 & 0.197 & 0.000 & 0.030 \\
			Iris & 0.342 & 0.621 & 0.238 & -0.285 & 0.730 & 0.607 & 0.244 & 0.684 \\
			Monk2 & 0.270 & 0.815 & 0.421 & 0.982 & 0.072 & 0.094 & -0.002 & 0.007 \\
			Moons & 0.272 & 0.968 & 0.277 & - & 0.241 & 0.319 & 0.785 & 0.092 \\
			Saheart & 0.265 & 0.800 & 0.147 & 0.974 & 0.018 & 0.020 & 0.068 & 0.000 \\
			Sonar & 0.116 & 0.649 & 0.124 & - & 0.004 & 0.013 & 0.000 & 0.000 \\
			Soybean & 0.515 & 0.304 & 0.496 & 0.503 & 0.545 & 0.621 & 0.000 & 0.244 \\
			Spectfheart & 0.343 & 0.896 & 0.334 & - & -0.107 & -0.114 & 0.000 & 0.050 \\
			Spiral & 0.114 & 0.856 & 0.058 & - & -0.003 & 0.012 & 0.034 & -0.002 \\
			Tae & 0.024 & 0.031 & 0.018 & - & 0.009 & -0.000 & 0.067 & 0.000 \\
			Vowel & 0.002 & 0.002 & 0.003 & - & 0.063 & -0.003 & 0.067 & - \\
			Zoo & 0.098 & 0.151 & 0.105 & 0.715 & 0.666 & 0.412 & 0.335 & - \\
			\hline
			Mean & 0.162 & \textbf{0.533} & 0.165 & -0.527 & 0.199 & 0.199 & 0.125 & -0.132 \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lcccccccc}
			\hline
			Dataset & \acs{SHADE}$_{CC}$ & \acs{DILS}$_{CC}$ & \acs{BRKGA}$_{CC}$ & \acs{COPKM} & \acs{LCVQE} & \acs{RDPM} & \acs{TVClust} & \acs{CECM} \\
			\hline
			Appendicitis & 0.332 & 0.957 & 0.296 & - & 0.305 & 0.284 & 0.025 & -0.006 \\
			Breast Cancer & 0.911 & 0.788 & 0.772 & 1.000 & 0.486 & 0.502 & 0.000 & 0.037 \\
			Bupa & 0.801 & 0.984 & 0.840 & 1.000 & -0.005 & -0.007 & -0.007 & 0.001 \\
			Circles & 0.982 & 1.000 & 0.828 & 1.000 & -0.003 & 0.375 & 0.973 & 0.105 \\
			Ecoli & 0.025 & 0.134 & 0.015 & - & 0.387 & 0.372 & 0.719 & - \\
			Glass & 0.031 & 0.057 & 0.017 & - & 0.280 & 0.253 & 0.229 & - \\
			Haberman & 0.796 & 1.000 & 0.866 & 1.000 & -0.002 & 0.075 & 0.219 & -0.050 \\
			Hayesroth & 0.099 & 0.386 & 0.107 & - & 0.106 & 0.107 & 0.150 & 0.135 \\
			Ionosphere & 0.591 & 0.970 & 0.803 & 1.000 & 0.178 & 0.212 & 0.000 & 0.057 \\
			Iris & 0.260 & 0.850 & 0.412 & - & 0.730 & 0.547 & 0.421 & 0.684 \\
			Monk2 & 0.945 & 0.902 & 0.751 & 1.000 & 0.072 & 0.170 & -0.002 & 0.007 \\
			Moons & 0.995 & 1.000 & 0.958 & 1.000 & 0.241 & 0.436 & 0.987 & 0.095 \\
			Saheart & 0.945 & 0.862 & 0.749 & 1.000 & 0.020 & 0.037 & 0.221 & 0.000 \\
			Sonar & 0.890 & 0.981 & 0.800 & - & 0.004 & 0.019 & 0.000 & 0.000 \\
			Soybean & 0.422 & 0.469 & 0.428 & 0.584 & 0.545 & 0.605 & 0.000 & 0.000 \\
			Spectfheart & 0.778 & 1.000 & 0.924 & 0.983 & -0.107 & -0.117 & 0.000 & -0.070 \\
			Spiral & 0.949 & 1.000 & 0.847 & - & -0.003 & 0.014 & 0.006 & 0.051 \\
			Tae & 0.066 & 0.299 & 0.119 & - & 0.008 & -0.004 & 0.062 & 0.000 \\
			Vowel & 0.001 & 0.003 & 0.002 & - & 0.063 & -0.003 & 0.073 & - \\
			Zoo & 0.128 & 0.185 & 0.157 & 0.435 & 0.642 & 0.450 & 0.353 & - \\
			\hline
			Mean & 0.547 & \textbf{0.691} & 0.535 & 0.05 & 0.197 & 0.216 & 0.221 & -0.148 \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lcccccccc}
			\hline
			Dataset & \acs{SHADE}$_{CC}$ & \acs{DILS}$_{CC}$ & \acs{BRKGA}$_{CC}$ & \acs{COPKM} & \acs{LCVQE} & \acs{RDPM} & \acs{TVClust} & \acs{CECM} \\
			\hline
			Appendicitis & 1.000 & 1.000 & 1.000 & - & 0.305 & 0.331 & 0.012 & -0.006 \\
			Breast Cancer & 0.977 & 0.807 & 0.807 & 1.000 & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & 0.993 & 0.991 & 0.936 & 1.000 & -0.005 & -0.007 & -0.006 & 0.000 \\
			Circles & 1.000 & 1.000 & 0.935 & 1.000 & -0.003 & 0.629 & 1.000 & 0.138 \\
			Ecoli & 0.047 & 0.201 & 0.028 & - & 0.387 & 0.459 & 0.763 & - \\
			Glass & 0.082 & 0.322 & 0.038 & - & 0.271 & 0.287 & 0.218 & - \\
			Haberman & 0.997 & 1.000 & 0.943 & 1.000 & -0.002 & 0.106 & 0.737 & 0.000 \\
			Hayesroth & 0.531 & 0.812 & 0.548 & - & 0.106 & 0.107 & 0.208 & 0.056 \\
			Ionosphere & 0.993 & 0.982 & 0.902 & 1.000 & 0.173 & 0.309 & 0.000 & 0.115 \\
			Iris & 0.553 & 0.968 & 0.691 & - & 0.708 & 0.540 & 0.585 & 0.684 \\
			Monk2 & 0.991 & 0.904 & 0.855 & 1.000 & 0.072 & 0.253 & -0.002 & 0.160 \\
			Moons & 0.995 & 1.000 & 0.937 & 1.000 & 0.241 & 0.831 & 1.000 & 0.180 \\
			Saheart & 0.981 & 0.881 & 0.881 & 1.000 & 0.018 & 0.026 & 1.000 & -0.006 \\
			Sonar & 1.000 & 1.000 & 0.992 & 1.000 & 0.004 & 0.127 & 0.000 & 0.003 \\
			Soybean & 0.563 & 0.564 & 0.416 & -0.218 & 0.545 & 0.631 & 0.000 & -0.016 \\
			Spectfheart & 1.000 & 1.000 & 0.953 & 1.000 & -0.107 & -0.112 & 0.000 & -0.054 \\
			Spiral & 0.998 & 1.000 & 0.921 & 1.000 & -0.003 & 0.011 & 0.006 & 0.045 \\
			Tae & 0.392 & 0.892 & 0.351 & - & 0.008 & 0.000 & 0.035 & 0.000 \\
			Vowel & 0.003 & 0.003 & 0.002 & - & 0.063 & -0.003 & 0.071 & - \\
			Zoo & 0.153 & 0.203 & 0.176 & 0.821 & 0.642 & 0.439 & 0.335 & - \\
			\hline
			Mean & 0.713 & \textbf{0.777} & 0.666 & 0.23 & 0.195 & 0.273 & 0.298 & -0.135 \\
			\hline

>>>>

This chapter presents the results obtained by the two new proposals introduced in this work (in Chapter \ref{ch:NewProposals}) and those obtained by the state-of-the-art. Being the mentioned the main purpose of this chapter, we firstly introduce a brief study on the influence of the parameter $\xi$ in the \acs{DILS} method in Section \ref{sec:XiInfl}, so the reader gets a better comprehension of theory presented in Section \ref{sec:DILS}. Afterwards we will carry out an in-depth comparison between \acs{BRKGA}$_{CC}$ and \acs{SHADE}$_{CC}$ in Section \ref{sec:BRKGAvsSHADE}, as both are population-based and heuristic-guided methods. Finally, in Section \ref{sec:NewPropvsSOTA}  we will present a more general comparison that will include all state-of-the-art methods and the new proposals.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.2}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{l ccc c ccc}
			\hline
			\multirow{2}{*}{Dataset} &
			\multicolumn{3}{c}{\acs{BRKGA}$_{CC}$} &&  \multicolumn{3}{c}{\acs{SHADE}$_{CC}$} \\
			\cline{2-4} \cline{6-8}
			& \acs{ARI} & Unsat(\%) & Time(s) && \acs{ARI} & Unsat(\%) & Time(s) \\
			\hline
			Appendicitis & \textbf{1.000} & 0.000 & 389.905 && \textbf{1.000} & 0.000 & 371.579 \\
			Breast Cancer & 0.807 & 9.086 & 4061.162 && \textbf{0.977} & 0.891 & 3984.370 \\
			Bupa & 0.936 & 2.975 & 1529.151 && \textbf{0.993} & 0.281 & 1508.772 \\
			Circles & 0.935 & 2.814 & 1180.268 && \textbf{1.000} & 0.000 & 1170.452 \\
			Ecoli & 0.028 & 25.716 & 1267.419 && \textbf{0.047} & 21.466 & 1277.903 \\
			Glass & 0.038 & 23.610 & 766.861 && \textbf{0.082} & 16.412 & 796.162 \\
			Haberman & 0.943 & 2.073 & 1266.131 && \textbf{0.997} & 0.138 & 1235.441 \\
			Hayesroth & \textbf{0.548} & 6.331 & 554.339 && 0.531 & 7.056 & 540.585 \\
			Ionosphere & 0.902 & 4.314 & 2051.251 && \textbf{0.993} & 0.258 & 2019.558 \\
			Iris & \textbf{0.691} & 5.241 & 513.675 && 0.553 & 6.528 & 488.262 \\
			Monk2 & 0.855 & 6.025 & 2055.425 && \textbf{0.991} & 0.379 & 2013.468 \\
			Moons & 0.937 & 2.689 & 1177.848 && \textbf{0.995} & 0.158 & 1157.222 \\
			Saheart & 0.881 & 5.250 & 2402.513 && \textbf{0.981} & 0.706 & 2353.931 \\
			Sonar & 0.992 & 0.186 & 1138.769 && \textbf{1.000} & 0.000 & 1127.020 \\
			Soybean & 0.416 & 0.000 & 171.281 && \textbf{0.563} & 0.000 & 153.406 \\
			Spectfheart & 0.953 & 1.677 & 1602.229 && \textbf{1.000} & 0.000 & 1526.925 \\
			Spiral & 0.921 & 3.604 & 1178.580 && \textbf{0.998} & 0.091 & 1155.194 \\
			Tae & 0.351 & 9.807 & 527.292 && \textbf{0.392} & 9.419 & 508.610 \\
			Vowel & 0.002 & 14.682 & 5450.331 && \textbf{0.003} & 13.766 & 5514.052 \\
			Zoo & \textbf{0.176} & 5.429 & 335.715 && 0.153 & 4.191 & 320.186 \\
			\hline
			Mean & 0.666 & 6.575 & 1481.007 && \textbf{0.713} & 4.087 & 1461.155 \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.2}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lcccccccc}
			\hline
			Dataset & \acs{SHADE}$_{CC}$ & \acs{DILS}$_{CC}$ & \acs{BRKGA}$_{CC}$ & \acs{COPKM} & \acs{LCVQE} & \acs{RDPM} & \acs{TVClust} & \acs{CECM} \\
			\hline
			Appendicitis & 0.086 & \textbf{0.611} & 0.022 & - & 0.335 & 0.316 & 0.025 & -0.005 \\
			Breast Cancer & 0.159 & \textbf{0.755} & 0.395 & -0.604 & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & 0.104 & \textbf{0.870} & 0.281 & - & -0.005 & -0.005 & -0.004 & -0.011 \\
			Circles & 0.063 & \textbf{0.798} & 0.166 & - & -0.003 & 0.162 & 0.137 & 0.133 \\
			Ecoli & 0.020 & 0.069 & 0.009 & - & 0.387 & \textbf{0.417} & 0.265 & - \\
			Glass & 0.013 & 0.009 & 0.016 & 0.184 & \textbf{0.268} & 0.197 & 0.211 & - \\
			Haberman & 0.084 & \textbf{0.638} & 0.047 & - & -0.002 & 0.127 & 0.218 & -0.004 \\
			Hayesroth & 0.025 & 0.031 & 0.027 & - & 0.106 & 0.097 & 0.054 & \textbf{0.139} \\
			Ionosphere & 0.332 & \textbf{0.792} & 0.125 & - & 0.168 & 0.197 & 0.000 & 0.030 \\
			Iris & 0.342 & 0.621 & 0.238 & -0.285 & \textbf{0.730} & 0.607 & 0.244 & 0.684 \\
			Monk2 & 0.270 & 0.815 & 0.421 & \textbf{0.982} & 0.072 & 0.094 & -0.002 & 0.007 \\
			Moons & 0.272 & \textbf{0.968} & 0.277 & - & 0.241 & 0.319 & 0.785 & 0.092 \\
			Saheart & 0.265 & 0.800 & 0.147 & \textbf{0.974} & 0.018 & 0.020 & 0.068 & 0.000 \\
			Sonar & 0.116 & \textbf{0.649} & 0.124 & - & 0.004 & 0.013 & 0.000 & 0.000 \\
			Soybean & 0.515 & 0.304 & 0.496 & 0.503 & 0.545 & \textbf{0.621} & 0.000 & 0.244 \\
			Spectfheart & 0.343 & \textbf{0.896} & 0.334 & - & -0.107 & -0.114 & 0.000 & 0.050 \\
			Spiral & 0.114 & \textbf{0.856} & 0.058 & - & -0.003 & 0.012 & 0.034 & -0.002 \\
			Tae & 0.024 & 0.031 & 0.018 & - & 0.009 & -0.000 & \textbf{0.067} & 0.000 \\
			Vowel & 0.002 & 0.002 & 0.003 & - & 0.063 & -0.003 & \textbf{0.067} & - \\
			Zoo & 0.098 & 0.151 & 0.105 & \textbf{0.715} & 0.666 & 0.412 & 0.335 & - \\
			\hline
			Mean & 0.162 & \textbf{0.533} & 0.165 & -0.527 & 0.199 & 0.199 & 0.125 & -0.132 \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lcccccccc}
			\hline
			Dataset & \acs{SHADE}$_{CC}$ & \acs{DILS}$_{CC}$ & \acs{BRKGA}$_{CC}$ & \acs{COPKM} & \acs{LCVQE} & \acs{RDPM} & \acs{TVClust} & \acs{CECM} \\
			\hline
			Appendicitis & 0.332 & \textbf{0.957} & 0.296 & - & 0.305 & 0.284 & 0.025 & -0.006 \\
			Breast Cancer & 0.911 & 0.788 & 0.772 & \textbf{1.000} & 0.486 & 0.502 & 0.000 & 0.037 \\
			Bupa & 0.801 & 0.984 & 0.840 & \textbf{1.000} & -0.005 & -0.007 & -0.007 & 0.001 \\
			Circles & 0.982 & \textbf{1.000} & 0.828 & \textbf{1.000} & -0.003 & 0.375 & 0.973 & 0.105 \\
			Ecoli & 0.025 & 0.134 & 0.015 & - & 0.387 & 0.372 & \textbf{0.719} & - \\
			Glass & 0.031 & 0.057 & 0.017 & - & \textbf{0.280} & 0.253 & 0.229 & - \\
			Haberman & 0.796 & \textbf{1.000} & 0.866 & \textbf{1.000} & -0.002 & 0.075 & 0.219 & -0.050 \\
			Hayesroth & 0.099 & \textbf{0.386} & 0.107 & - & 0.106 & 0.107 & 0.150 & 0.135 \\
			Ionosphere & 0.591 & 0.970 & 0.803 & \textbf{1.000} & 0.178 & 0.212 & 0.000 & 0.057 \\
			Iris & 0.260 & \textbf{0.850} & 0.412 & - & 0.730 & 0.547 & 0.421 & 0.684 \\
			Monk2 & 0.945 & 0.902 & 0.751 & \textbf{1.000} & 0.072 & 0.170 & -0.002 & 0.007 \\
			Moons & 0.995 & \textbf{1.000} & 0.958 & \textbf{1.000} & 0.241 & 0.436 & 0.987 & 0.095 \\
			Saheart & 0.945 & 0.862 & 0.749 & \textbf{1.000} & 0.020 & 0.037 & 0.221 & 0.000 \\
			Sonar & 0.890 & \textbf{0.981} & 0.800 & - & 0.004 & 0.019 & 0.000 & 0.000 \\
			Soybean & 0.422 & 0.469 & 0.428 & 0.584 & 0.545 & \textbf{0.605} & 0.000 & 0.000 \\
			Spectfheart & 0.778 & \textbf{1.000} & 0.924 & 0.983 & -0.107 & -0.117 & 0.000 & -0.070 \\
			Spiral & 0.949 & \textbf{1.000} & 0.847 & - & -0.003 & 0.014 & 0.006 & 0.051 \\
			Tae & 0.066 & \textbf{0.299} & 0.119 & - & 0.008 & -0.004 & 0.062 & 0.000 \\
			Vowel & 0.001 & 0.003 & 0.002 & - & 0.063 & -0.003 & \textbf{0.073} & - \\
			Zoo & 0.128 & 0.185 & 0.157 & 0.435 & \textbf{0.642} & 0.450 & 0.353 & - \\
			\hline
			Mean & 0.547 & \textbf{0.691} & 0.535 & 0.05 & 0.197 & 0.216 & 0.221 & -0.148 \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lcccccccc}
			\hline
			Dataset & \acs{SHADE}$_{CC}$ & \acs{DILS}$_{CC}$ & \acs{BRKGA}$_{CC}$ & \acs{COPKM} & \acs{LCVQE} & \acs{RDPM} & \acs{TVClust} & \acs{CECM} \\
			\hline
			Appendicitis & \textbf{1.000} & \textbf{1.000} & \textbf{1.000} & - & 0.305 & 0.331 & 0.012 & -0.006 \\
			Breast Cancer & 0.977 & 0.807 & 0.807 & \textbf{1.000} & 0.486 & 0.502 & 0.000 & 0.000 \\
			Bupa & 0.993 & 0.991 & 0.936 & \textbf{1.000} & -0.005 & -0.007 & -0.006 & 0.000 \\
			Circles & \textbf{1.000} & \textbf{1.000} & 0.935 & \textbf{1.000} & -0.003 & 0.629 & \textbf{1.000} & 0.138 \\
			Ecoli & 0.047 & 0.201 & 0.028 & - & 0.387 & 0.459 & \textbf{0.763} & - \\
			Glass & 0.082 & \textbf{0.322} & 0.038 & - & 0.271 & 0.287 & 0.218 & - \\
			Haberman & 0.997 & \textbf{1.000} & 0.943 & \textbf{1.000} & -0.002 & 0.106 & 0.737 & 0.000 \\
			Hayesroth & 0.531 & \textbf{0.812} & 0.548 & - & 0.106 & 0.107 & 0.208 & 0.056 \\
			Ionosphere & 0.993 & 0.982 & 0.902 & \textbf{1.000} & 0.173 & 0.309 & 0.000 & 0.115 \\
			Iris & 0.553 & \textbf{0.968} & 0.691 & - & 0.708 & 0.540 & 0.585 & 0.684 \\
			Monk2 & 0.991 & 0.904 & 0.855 & \textbf{1.000} & 0.072 & 0.253 & -0.002 & 0.160 \\
			Moons & 0.995 & \textbf{1.000} & 0.937 & \textbf{1.000} & 0.241 & 0.831 & \textbf{1.000} & 0.180 \\
			Saheart & 0.981 & 0.881 & 0.881 & \textbf{1.000} & 0.018 & 0.026 & \textbf{1.000} & -0.006 \\
			Sonar & \textbf{1.000} & \textbf{1.000} & 0.992 & \textbf{1.000} & 0.004 & 0.127 & 0.000 & 0.003 \\
			Soybean & 0.563 & 0.564 & 0.416 & -0.218 & 0.545 & \textbf{0.631} & 0.000 & -0.016 \\
			Spectfheart & \textbf{1.000} & \textbf{1.000} & 0.953 & \textbf{1.000} & -0.107 & -0.112 & 0.000 & -0.054 \\
			Spiral & 0.998 & \textbf{1.000} & 0.921 & \textbf{1.000} & -0.003 & 0.011 & 0.006 & 0.045 \\
			Tae & 0.392 & \textbf{0.892} & 0.351 & - & 0.008 & 0.000 & 0.035 & 0.000 \\
			Vowel & 0.003 & 0.003 & 0.002 & - & 0.063 & -0.003 & \textbf{0.071} & - \\
			Zoo & 0.153 & 0.203 & 0.176 & \textbf{0.821} & 0.642 & 0.439 & 0.335 & - \\
			\hline
			Mean & 0.713 & \textbf{0.777} & 0.666 & 0.23 & 0.195 & 0.273 & 0.298 & -0.135 \\
			\hline

### 2019-06-30 Memoria/Chapters/ExperimentalSetup.tex
Acabada memoria excepto conclusiones y trabajo futuro

\begin{equation}
\text{Rand}(C_1, C_2) = \frac{a + b}{n(n - 1)/2}
\label{eq15}
\end{equation}

@@

\begin{equation}
\text{ARI}(C_1, C_2) = \frac{\text{Rand}(C_1, C_2) - \text{Expected Index}}{\text{Maximum Index} - \text{Expected Index}},
\label{eq16}
\end{equation}

@@

In order to validate the results which will be presented in Section \ref{sec:results} we will use Bayesian statistical tests, instead of the classic \acf{NHST}. In \cite{benavoli2017time} we find an in-depth analysis of the disadvantages of \acs{NHST}, and a new model is proposed for carrying out comparisons researchers are interested in. \textit{"In a nutshell: \acs{NHST} do not answer the question we ask"}. To put it clear, the disadvantages of the \acs{NHST} that the authors highlight in \cite{benavoli2017time} are based on the trap of black-and-white thinking, this is: to reject, or not to reject?

@@

Table \ref{tab:paramsDILS} shows a summary of the parameter setup used for the \acs{DILS}$_{CC}$ method.

@@

In all three cases---\acs{BRKGA}$_{CC}$, \acs{SHADE}$_{CC}$ and \acs{DILS}$_{CC}$---the stop criterion is given by the number of evaluations of the fitness function, which at most will be 300000. To compare with the state-of-the-art methods mentioned in Section \ref{sec:SOTA} we will use the parameters setup shown in Table \ref{tab:paramsSOTA}.

@@

Parameter values have been assigned following the guidelines of the original creators of the different proposals. Since the evaluation in the experimental stage makes use of a high number of datasets, tuning each parameter specifically for each dataset is not feasible. Indeed, our goal is not optimization in a case-by-case basis but instead a comparison in the most general scenario possible. Therefore, given that the purpose of this work is to draw a fair comparison between the algorithms and assess their robustness in a common environment with multiple datasets, we have not included a tuning step to maximize any particular performance metric. All parameters described above are ment to be used for the implementation that can be found at \href{https://github.com/GermangUgr}{GitHub}\footnote{https://github.com/GermangUgr}.

>>>>

\begin{equation}
\text{Rand}(C_1, C_2) = \frac{a + b}{n(n - 1)/2}.
\label{eq15}
\end{equation}

@@

\begin{equation}
\text{ARI}(C_1, C_2) = \frac{\text{Rand}(C_1, C_2) - \text{Expected Index}}{\text{Maximum Index} - \text{Expected Index}}\;\;,
\label{eq16}
\end{equation}

@@

In order to validate the results which will be presented in Chapter \ref{ch:ExperimentalResults} we will use Bayesian statistical tests, instead of the classic \acf{NHST}. In \cite{benavoli2017time} we find an in-depth analysis of the disadvantages of \acs{NHST}, and a new model is proposed for carrying out comparisons researchers are interested in. \textit{"In a nutshell: \acs{NHST} do not answer the question we ask"}. To put it clear, the disadvantages of the \acs{NHST} that the authors highlight in \cite{benavoli2017time} are based on the trap of black-and-white thinking, this is: to reject, or not to reject?

@@

Table \ref{tab:paramsDILS} shows a summary of the parameter setup used for the \acs{DILS}$_{CC}$ method. All parameters related to the new proposals---\acs{SHADE}$_{CC}$ and \acs{DILS}$_{CC}$---have been set experimentally, no theoretical or in-depth experimental analysis have been carried out to find an optimal tune for them.

@@

In all three cases---\acs{BRKGA}$_{CC}$, \acs{SHADE}$_{CC}$ and \acs{DILS}$_{CC}$---the stopping criterion is given by the number of evaluations of the fitness function, which at most will be 300000. To compare with the state-of-the-art methods mentioned in Section \ref{sec:SOTA} we will use the parameters setup shown in Table \ref{tab:paramsSOTA}.

@@

Parameter values have been assigned following the guidelines of the original creators of the different proposals. Since the evaluation in the experimental stage makes use of a high number of datasets, tuning each parameter specifically for each dataset is not feasible. Indeed, our goal is not optimization in a case-by-case basis but instead a comparison in the most general scenario possible. Therefore, given that the purpose of this work is to draw a fair comparison between the algorithms and assess their robustness in a common environment with multiple datasets, we have not included a tuning step to maximize any particular performance metric. All parameters described above are meant to be used for the Python implementation that can be found at \href{https://github.com/GermangUgr}{GitHub}\footnote{https://github.com/GermangUgr}, which will be used to obtain our results.

### 2019-06-30 Memoria/Chapters/Introduction.tex
Acabada memoria excepto conclusiones y trabajo futuro

@@

>>>>

\section{Objectives}

The main objective of this work is to provide an overview of the concepts and particularities related to constrained clustering. Some of these concepts must be addressed with sufficient depth, in order for the reader to be able to easily understand the new approaches to constrained clustering contained in this work. It is also of our interest to provide an example of proper experimental methodology to obtain relevant and objectivity-free conclusions.

@@

Regarding the organization of this work, background knowledge concerning classic clustering and constrained clustering will be presented in Chapters \ref{ch:IntroClustering} and \ref{ch:ConstrainedClustering} respectively. In Chapter \ref{ch:NewProposals} two new approaches to the constrained clustering problem are discussed. The experimental setup to carry out the experiments to test them and their results are presented in Chapters \ref{ch:ExperimentalSetup} and \ref{ch:ExperimentalResults} respectively. Afterward an empirical analysis of these results is performed in Chapter \ref{ch:AnalysisResults}. Finally conclusions and future work are discussed in Chapter \ref{ch:ConclFW}.

### 2019-06-30 Memoria/FrontBackmatter/Abstract.tex
Acabada memoria excepto conclusiones y trabajo futuro

>>>>

Clustering has always been a powerful tool in knowledge discovery. Traditionally unsupervised, it received renewed attention when it was shown to produce better results when provided with new types of information, thus leading to a new kind of semi-supervised learning: constrained clustering. This technique is a generalization of traditional clustering that considers additional information encoded by constraints. Constraints can be given in the form of instance-level must-link and cannot-link constraints, which this paper focuses on. We propose the first application of Differential Evolution to the constrained clustering problem, as well as a new Local Search variant and its application to the problem at hands. We will compare the results obtained by these new proposals to those obtained by the state-of-the-art algorithms on twenty datasets with incremental levels of constraint-based information, supporting our conclusions with the aid of Bayesian statistical tests.\\

\noindent\textbf{Keywords:} constrained clustering, instance-level, must-link, cannot-link, differential evolution, local search.
